|

### 2022-06-22 docs/rmd/paper.Rmd
autogit

Table 9 displays the resulting P-values from computing the MWU test in a matrix format. The results demonstrate a highly significant difference int

@@

The mean overall performance of tournament selection appears to be superior to that of $\epsilon$-Lexicase selection which could be considered contradictory evidence to the 
... interpretation...

To further examine the generalization behaviour based on both selection operators I plotted the mean fitness scores for both algorithms in figure 2.

@@

... interpretation...

>>>>

Table 9 displays the resulting p-values from computing the MWU test in a matrix format.

@@

The results show two major findings:

1. The differences in mean fitness between tournament selection and $\epsilon$-Lexicase selection are highly statistical significant even if considering an $\alpha$ of 0.01. For the given symbolic regression task tournament selection achieves a better mean performance on both the training as well as the testing dataset than $\epsilon$-Lexicase selection. These findings contradict the hypothesis $H0_{1}$ descibed in subsection 3.1 and are contrary to some of the research that was summarized in subsections 2.1 and 2.3.[@epsilon_lexicase_main] [@https://doi.org/10.48550/arxiv.1709.05394].

2. The differences in mean fitness between $min\_training\_error$ and $testing\_error$ are not statistically significant for both selection algorithms. If comparing the mean training error to the mean testing error, the p-values only computes to 0.309 for tournament selection and to 0.257 for $\epsilon$-Lexicase selection. These findings fail to reject $H0_{2}$, based on the obtained results we can not find evidence that both algorithms demonstrate a significantly different performance between the training data and the previously unseen testing data.

To further examine the generalization behaviour of both selection operators I plotted the mean fitness scores for both algorithms over the total number of 100 generations in figure 2. Figure 2 shows that both algorithms show little visual evidence of overfitting which would result in a growing gap between between $min\_training\_error$ and $testing\_error$ in the final stages of the evolutionary optimization. For $\epsilon$-Lexicase selection a small gap can be observed starting at around the 90.th generation, while the minimum training error slowly converges a small increase in the testing error can be observed. Based on the limited amount of collected data, it is questionable if this small sign of overfitting can be interpreted as a weak indicator for an inferior generalization behaviour of $\epsilon$-Lexicase in comparison to tournament selection.

Figure 2 also shows a visual representation of the described overall performance benefit of using tournament selection instead of $\epsilon$-Lexicase selection for the choosen symbolic regression task. It can be observed that at all stages of the evolution tournament selection based GP achieves a lower mean error for both datasets.

@@

### 2022-06-22 docs/rmd/paper.tex
autogit

The results of the MWU test are summarized in table 9.

@@

The mean overall performance of tournament selection appears to be
superior to that of \(\epsilon\)-Lexicase selection which could be
considered contradictory evidence to the \ldots{} interpretation\ldots{}

To further examine the generalization behaviour based on both selection
operators I plotted the mean fitness scores for both algorithms in
figure 2.

@@

\ldots{} interpretation\ldots{}

>>>>

Table 9 displays the resulting p-values from computing the MWU test in a
matrix format.

@@

The results show two major findings:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  The differences in mean fitness between tournament selection and
  \(\epsilon\)-Lexicase selection are highly statistical significant
  even if considering an \(\alpha\) of 0.01. For the given symbolic
  regression task tournament selection achieves a better mean
  performance on both the training as well as the testing dataset than
  \(\epsilon\)-Lexicase selection. These findings contradict the
  hypothesis \(H0_{1}\) descibed in subsection 3.1 and are contrary to
  some of the research that was summarized in subsections 2.1 and
  2.3.(La Cava, Spector and Danai, 2016) (La Cava \emph{et al.}, 2017).
\item
  The differences in mean fitness between \(min\_training\_error\) and
  \(testing\_error\) are not statistically significant for both
  selection algorithms. If comparing the mean training error to the mean
  testing error, the p-values only computes to 0.309 for tournament
  selection and to 0.257 for \(\epsilon\)-Lexicase selection. These
  findings fail to reject \(H0_{2}\), based on the obtained results we
  can not find evidence that both algorithms demonstrate a significantly
  different performance between the training data and the previously
  unseen testing data.
\end{enumerate}

To further examine the generalization behaviour of both selection
operators I plotted the mean fitness scores for both algorithms over the
total number of 100 generations in figure 2. Figure 2 shows that both
algorithms show little visual evidence of overfitting which would result
in a growing gap between between \(min\_training\_error\) and
\(testing\_error\) in the final stages of the evolutionary optimization.
For \(\epsilon\)-Lexicase selection a small gap can be observed starting
at around the 90.th generation, while the minimum training error slowly
converges a small increase in the testing error can be observed. Based
on the limited amount of collected data, it is questionable if this
small sign of overfitting can be interpreted as a weak indicator for an
inferior generalization behaviour of \(\epsilon\)-Lexicase in comparison
to tournament selection.

Figure 2 also shows a visual representation of the described overall
performance benefit of using tournament selection instead of
\(\epsilon\)-Lexicase selection for the choosen symbolic regression
task. It can be observed that at all stages of the evolution tournament
selection based GP achieves a lower mean error for both datasets.

@@
